Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Better explanation of yellow parts in caption for first approach figure
Split up discussion of libraries in implementation section
Say what SVG means
Mention implementation will work with OpenGL 4 too

The two approaches were implemented using OpenGL with C++.  To ensure results
are relevant to current and future applications, we used only the core profile
of OpenGL 3.  In other words, no deprecated functionality from OpenGL 2 was
used.

To facilitate the process, a handful of general-purpose graphics libraries were
developed.  At the lowest levels are a simple 3D mathematics library and a
library providing thin C++ wrappers around the components already in OpenGL.
Above that, another library provides additional utilities for working with
OpenGL, including one for loading volumetric data as a texture.  At the highest
level is a library providing a simple render graph that can be used to rapidly
prototype OpenGL applications.  Similar to SVG, the render graph can be written
in XML so scenes can easily be saved, reloaded, and shared.  All of the
libraries can be compiled as shared libraries using GCC on Linux and Mac OS X.

>>>>

The two approaches were implemented using OpenGL with C++.  To ensure results
are relevant to current and future applications, we used only the core profile
of OpenGL 3.  In other words, no deprecated functionality from OpenGL 2 was
used.  Furthermore, because OpenGL 4 is a superset of the OpenGL 3 core profile,
the implementation will easily work with that as well.

To facilitate the process, a handful of general-purpose graphics libraries were
developed.

At the lowest levels are a simple 3D mathematics library and a library providing
thin C++ wrappers around the components already in OpenGL.  Above that, another
library provides additional utilities for working with OpenGL, including one for
loading volumetric data as a texture.

At the highest level is a library providing a simple render graph that can be
used to rapidly prototype OpenGL applications.  Similar to SVG, or Scalable
Vector Graphics, the render graph can be written in XML so scenes can easily be
saved, reloaded, and shared.

All of the libraries can be compiled as shared libraries using GCC on Linux and
Mac OS X.
